Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-19 ms.tex
cleaning up description of uncertainties

This error budget is modeled after \cite{planckdust} Equation 7, but with some 
modifications and additions. The first term accounts for the multiplicative 
uncertainty on the input maps. Table \ref{table:offs} lists the multiplicative 
calibration uncertainty $c_{\nu}$ for each band. These values are taken from 
Table 11 of \cite{planckcalib}. The second term represents an uncertainty due 
to our subtraction of the \verb|SMICA| CMB model. The analogous term in 
\cite{planckdust} Equation 7 is ($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. 
an uncertainty proportional to the CMB model amplitude in each pixel. Because 
this term's spatial dependence can imprint the CMB anisotropies on the derived 
parameters, we have chosen to replace \verb|SMICA|($p$) with a spatially 
constant, RMS value for the CMB amplitude, $\sigma_{CMB}$. Table 
\ref{table:offs} lists the adopted values of $\sigma_{CMB}$. $\delta O_{\nu_i}$
represents the uncertainty in the band $\nu_i$ zero level offset, and the 
values of $\delta O_{\nu_i}$ can be read off from the second column of Table 
\ref{table:offs}. $n_{\nu_i}$ represents the instrumental noise in band 
$\nu_i$. Because using per-pixel noise estimates based on the \verb|ii_cov| 
parameter can imprint sharp-edged features of the survey pattern onto the 
derived parameters, we have adopted a conservative, spatially constant value of
$n_{\nu_i}$ for each band. Table \ref{table:offs} lists the values of 
$n_{\nu_i}$ adopted. The next term accounts for the uncertainty on the CO 
emission correction, taking $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$ 
(see $\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).

>>>>

This error budget is modeled after \cite{planckdust} Equation 7, but with some 
modifications and additions. The first term accounts for the multiplicative 
uncertainty on the input maps. Table \ref{table:offs} lists the multiplicative 
calibration uncertainty $c_{\nu}$ for each band. These values are taken from 
Table 11 of \cite{planckcalib}. The second term represents an uncertainty due 
to our subtraction of the \verb|SMICA| CMB model. The analogous term in 
\cite{planckdust} Equation 7 is ($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. 
an uncertainty proportional to the CMB model amplitude in each pixel. Because 
this term's spatial dependence can imprint the CMB anisotropies on the derived 
parameters, we have chosen to replace \verb|SMICA|($p$) with a spatially 
constant, RMS value for the CMB amplitude, $\sigma_{CMB, \nu_i}$. 
$\delta O_{\nu_i}$ represents the uncertainty in the band $\nu_i$ zero level 
offset, and the values of $\delta O_{\nu_i}$ can be read off from the second 
column of Table \ref{table:offs}. $n_{\nu_i}$ represents the instrumental noise
in band $\nu_i$. Because using per-pixel noise estimates based on the \PLANCK~
\verb|ii_cov| parameter can imprint features of the survey pattern onto the 
derived parameters, we have adopted a conservative, spatially constant value of
$n_{\nu_i}$ for each band. These values of $n_{\nu_i}$ are listed in Table 
\ref{table:offs}. The next term accounts for the uncertainty on the CO emission
correction, taking $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$ (see 
$\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).
